Tracking $p$-adic precision

### 2014-05-22 padicprec.tex
Small fixes

\begin{deftn}
\label{def:firstorder}
Let $E$ and $F$ be two $K$-Banach spaces, $f : U \rightarrow F$ be a 
function defined on an open subset $U$ of $E$ and $v_0$ be a 
point in $U$.
A lattice $H$ in $E$ is called a \emph{first order lattice} for $f$ at 
$v_0$ if the following equality holds:
\begin{equation}
\label{eq:firstorder}
f(v_0 + H) = f(v_0) + f'(v_0) (H).
\end{equation}
\end{deftn}

@@

We recall that the Legendre transform of a \emph{convex} function 
$\varphi : \R \to \R \cup \{+\infty\}$ is the function $\varphi^\star : 
\R \to \R \cup \{+\infty\}$ defined by
\[
\textstyle \varphi^\star(v) = \sup_{u \in \R} \:
\big(uv - \varphi(u)\big),
\]
for $v \in \R$.
One can check that the map $\varphi \mapsto \varphi^\star$ is an
order-reversing involution: $(\varphi^\star)^\star = \varphi$ and
$\varphi^\star \geq \psi^\star$ whenever $\varphi \leq \psi$.
We refer to \cite{Rockafellar:97} for a complete exposition on Legendre transforms.

>>>>

\begin{deftn}
\label{def:firstorder}
Let $E$ and $F$ be two $K$-Banach spaces, $f : U \rightarrow F$ be a 
function defined on an open subset $U$ of $E$ and $v_0$ be a 
point in $U$.
A lattice $H$ in $E$ is called a \emph{first order lattice} for $f$ at 
$v_0$ if $v_0 + H \subset U$ and the following equality holds:
\begin{equation}
\label{eq:firstorder}
f(v_0 + H) = f(v_0) + f'(v_0) (H).
\end{equation}
\end{deftn}

@@

We recall that the Legendre transform of a \emph{convex} function 
$\varphi : \R \to \R \cup \{+\infty\}$ is the function $\varphi^\star : 
\R \to \R \cup \{+\infty\}$ defined by
\[
\textstyle \varphi^\star(v) = \sup_{u \in \R} \:
\big(uv - \varphi(u)\big),
\]
for $v \in \R$.
One can check that the map $\varphi \mapsto \varphi^\star$ is an
order-reversing involution: $(\varphi^\star)^\star = \varphi$ and
$\varphi^\star \geq \psi^\star$ whenever $\varphi \leq \psi$. When
necessary, we extend $\varphi^\star$ to $\R \cup \{+\infty\}$ by
left continuity.
We refer to \cite{Rockafellar:97} for a complete exposition on Legendre transforms.
